An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-03-11 poly-embed-journal/poly-embed-journal.tex
more lovasz edits

The authors show that actually determining this link is nontrivial: simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not calibrated, thus casting doubt on a simple trial-and-error approach for finding the link.
Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have unique geometric structure (Figure~\ref{fig:lovasz-links}).
Perhaps surprisingly, they prove that $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are both calibrated with respect to $\ellabs$, for \emph{any} submodular and increasing $f$.

>>>>

As the authors show, however, actually determining this link function is nontrivial.
Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
Instead, they leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
Perhaps surprisingly, they prove that both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for \emph{any} submodular and increasing $f$.
